Word Sense Disambiguation\\ \small{Leveraging the NLTK Toolkit and External Tools}

### 2011-04-14 paper/paper.tex

%\begin{figure}[H]
%\includegraphics[width=\textwidth]{pg_0001}
%\caption{\label{fig1}}
%\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

\begin{figure}[H]
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}}
\end{figure}

>>>>

\begin{figure}[h]
\includegraphics[width=\textwidth]{pg_0001}
\caption{\label{fig1}}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\textwidth]{pg_0003}
\caption{\label{fig3}}
\end{figure}

According to Figure \ref{fig3}, when the base word feature vector was
enabled and the dependency parsing was disabled, the \naive{} Bayes
classifier improved in performance. On the other hand, the performance
of the Decision Tree classifier seems to be independent of the base
word and dependency parsing features.

\begin{figure}
\includegraphics[width=\textwidth]{pg_0004}
\caption{\label{fig4}}
\end{figure}
